The Astropy Project:

### 2017-09-21 main.tex
Update on Overleaf.

\section*{Notes and guidelines (\textit{to be removed})}

\begin{itemize}
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
    \item Use \escapecmd{\sectionname} not Section, \escapecmd{\figname} not Figure, \escapecmd{\documentname} not Article
\end{itemize}

@@

\section{Major concepts}

@@

\subsection{Coordinates}
% Adrian & Erik

The \texttt{astropy.coordinates} subpackage is designed to support

@@

\subsection{Statistics}
% Steve C. and Jake V.

@@

\section{Learning Astropy}
% Kelle & Adrian?

>>>>

\section*{\textit{Notes and guidelines (to be removed)}}

\begin{itemize}
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
\end{itemize}

@@

\section{Major concepts}
% Anyone want to take this??

@@

\subsection{Coordinates}
% Adrian, Erik

The \texttt{astropy.coordinates} subpackage is designed to support representing and transforming celestial coordinates and velocities.

@@

\subsection{Statistics}
% Steve C., Jake V.

@@

\section{Learning Astropy}
% Kelle, Adrian
